Appendix

### 2022-05-02 paper/appendix.Rmd
semeff results + results + discussion

>>>>

## Proportion and number of piscivorous species

```{r}
loadd(rigal_classification, st_mono_trends_stable_rich_bm, full_data2)
full_data2 %>%
  select(richness, nb_pisc_rich, nb_non_pisc_rich)
unique(rigal_classification$variable)
var_pisc_mod <- c("nb_pisc_rich_std", "prop_pisc_rich", "nb_non_pisc_rich_std",
    "prop_non_pisc_rich",
      "log_rich_std", "log_bm_std")
pisc_data <- map(var_pisc_mod,
    function(x, var_to_keep, classif_var) {

      x_data <- classif_var[classif_var$variable == x, ] %>%
	unnest(classif)
      x_data <- x_data[, colnames(x_data) %in% var_to_keep]

      # Rename according to the variable
      colnames(x_data)[colnames(x_data) %in% var_to_keep[2:3]] <-
	paste0(x, c("", "_strd_error"))
      return(x_data)

    },
    var_to_keep = c("station", "linear_slope", "linear_slope_strd_error"),
  classif_var = rigal_classification) %>%
  Reduce(merge.all, .) %>%
  filter(station %in% st_mono_trends_stable_rich_bm) %>%
  na.omit()

# for standardized coefficients 
pisc_data_scaled <- pisc_data %>%
  mutate(across(all_of(var_pisc_mod), ~ scale(., center = FALSE)[,1]))

pisc_mod_std <- tibble(
  response = c("nb_pisc_rich_std", "nb_non_pisc_rich_std", "prop_pisc_rich", "prop_non_pisc_rich"),
  mod = list(
    lm(
      nb_pisc_rich_std ~ log_bm_std + log_rich_std,
      data = pisc_data_scaled,
      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
        nb_pisc_rich_std_strd_error)
      ),
    lm(
      nb_non_pisc_rich_std ~ log_bm_std + log_rich_std,
      data = pisc_data_scaled,
      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
        nb_non_pisc_rich_std_strd_error)
      ),
    lm(
      prop_pisc_rich ~ log_bm_std + log_rich_std,
      data = pisc_data_scaled,
      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
        prop_pisc_rich_strd_error)
      ),
    lm(
      prop_non_pisc_rich ~ log_bm_std + log_rich_std,
      data = pisc_data_scaled,
      weight = 1 / (log_rich_std_strd_error + log_bm_std_strd_error +
        prop_non_pisc_rich_strd_error)
      )
  )
  )

pisc_mod_std <- pisc_mod_std %>%
  mutate(
    coefs = map(mod, broom::tidy),
    perf = map(mod, broom::glance) 
  )

pisc_mod_std %>%
  select(response, coefs) %>%
  unnest(coefs)
```
